X-ray phase-contrast imaging at 100 keV on a conventional source

### 2013-11-29 hedpc.tex
restored siunitx with scriptscriptsize in the methods section

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
%\usepackage{pnastwof}

@@

%% Enter any subheads and the Materials and Methods text below.
\begin{materials}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD. The effective pixel size
is $\SI{80}{\micro \metre}$. The collimating slit right after the source is 
$\SI{25}{\micro \metre}$ large, while the second slit before the detector is
$\SI{100}{\micro\metre}$.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time was chosen in order to
get a low noise in the differential phase image. The SNR is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~\SI{14}{\percent} already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.
\end{materials}

@@

\begin{acknowledgments}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the SEM images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
\end{acknowledgments}

>>>>

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}
%\usepackage{pnastwof}

\DeclareMathSizes{10}{18}{12}{7}

@@

%% Enter any subheads and the Materials and Methods text below.
\begin{materials}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $\scriptscriptstyle 5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at $\scriptscriptstyle
\SI{100}{\kilo\electronvolt}$
is a symmetric Talbot-Lau interferometer with a grating period of $\scriptscriptstyle p = \SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\scriptscriptstyle \SI{32}{\centi\metre}$ and the source
grating is positioned $\scriptscriptstyle \SI{23}{\centi\metre}$ away from the source.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\scriptscriptstyle \SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\scriptscriptstyle \SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of $\scriptscriptstyle \SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD. The effective pixel size
is $\scriptscriptstyle \SI{80}{\micro \metre}$. The collimating slit right after the source is 
$\scriptscriptstyle \SI{25}{\micro \metre}$ large, while the second slit before the detector is
$\scriptscriptstyle \SI{100}{\micro\metre}$.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings ($\scriptscriptstyle \SI{5}{\percent}$). The exposure time was chosen in order to
get a low noise in the differential phase image. The SNR is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~$\scriptscriptstyle \SI{14}{\percent}$ already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.
\end{materials}

@@

\begin{acknowledgments}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the SEM images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'\'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
\end{acknowledgments}
